\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research

### 2025-03-07 paper.tex
text

\section{Explanation of "Universe"}
    \subsection*{AdS (Anti-de Sitter) Space $\Rightarrow$ The Bulk}
    \begin{itemize}
        \item The \textbf{bulk} represents a higher-dimensional space in the AdS/CFT framework.  
        \item A \textbf{surface} is a geometric object within AdS space that plays a crucial role in holography.  
        \item The \textbf{minimal area} surface, also known as the RT surface in AdS/CFT, spans the boundary subregion and has the smallest possible area.  
        \item Since direct calculations in the bulk are challenging due to quantum gravity, computations are instead performed on the CFT boundary.  
    \end{itemize}

@@

    \subsubsection*{Quick Notes about AdS and CFT}
    \begin{itemize}
        \item If dealing with 5-dimensional AdS bulk, the boundary is typically 4-dimensional, and the CFT lives on this 4-dimensional boundary.
        \item DBRP idea in physic terms:
        \begin{itemize}
            \item Because the CFT is a non-gravitational theory, it is easier to make computations and to understand. And because it lives on the boundary of the AdS space, we can use the CFT to reconstruct the gravitational dynamics of the AdS bulk.
            \item Given a CFT state, we can determine the corresponding spacetime that the CFT describes, including its geometry and gravitational dynamics.
            \item Then we can use entanglement entropy in the CFT to learn about spacetime geometry in the bulk.
        \end{itemize}
    \end{itemize}

>>>>

%%%%%%%%%%%%%%%% 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Explanation of "Universe"}
    \subsection*{AdS (Anti-de Sitter) Space $\Rightarrow$ The Bulk}
    \begin{itemize}
        \item The \textbf{bulk} represents a higher-dimensional space in the AdS/CFT framework.  
        \item A \textbf{surface} is a geometric object within AdS space that plays a crucial role in holography.  
        \item The \textbf{minimal area} surface, also known as the RT surface in AdS/CFT, spans the boundary subregion and has the smallest possible area.  
        \item Since direct calculations in the bulk are challenging due to quantum gravity, computations are instead performed on the CFT boundary.  
    \end{itemize}

@@

    %% Photo of AdS/ CFT space 
    \begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
        \centering
        \includegraphics[width=0.8\textwidth]{ads_cft.jpeg}  % Adjust width as needed
        \caption{This illustration shows the AdS/ CFT spacetime. Where a geodesic is a straight line across the hyperbolic disk, which is the shortest path between points. In the context of anti-de Sitter spacetime a geodesic represents the path that a particle follows when only affected by gravity.}  % Caption text
        \label{fig:example}  % Label for referencing
    \end{figure}

    When dealing with a 5-dimensional AdS bulk, the boundary is typically 4-dimensional, and the CFT lives on this 4-dimensional boundary. This is the idea that the boundary is 1 less dimension that the bulk. 
    The boundary is where we will make our computations. Because of the lack of gravity it is easier to compute and understand. We then can use the CFT computations to reconstruct the gravitational dynamics of the AdS bulk which translates to the geodesics of the hyperbolic disk. 
    \subsubsection*{Quick Notes about AdS and CFT}
    \begin{itemize}
        \item DBRP idea in physic terms:
        \begin{itemize}
            \item Because the CFT is a non-gravitational theory, it is easier to make computations and to understand. And because it lives on the boundary of the AdS space, we can use the CFT to reconstruct the gravitational dynamics of the AdS bulk.
            \item Given a CFT state, we can determine the corresponding spacetime that the CFT describes, including its geometry and gravitational dynamics.
            \item Then we can use entanglement entropy in the CFT to learn about spacetime geometry in the bulk.
        \end{itemize}
    \end{itemize}
